\name: Deterministic and Coherent Implicits

### 2018-06-20 jfp/src/Translation.tex
adapt notation in elaboration section

The function $\ttrans$ takes 
$\name$ types $\rulet$ to System F types T: 
\begin{equation*}
\begin{array}{rcl@{\hspace{1cm}}rcl}
\ttrans[\alpha] & = & \alpha &
\ttrans[\forall \alpha. \rulet] & = & \forall \alpha. \ttrans[\rulet] \\
\ttrans[\rulet_1 \arrow \rulet_2] & = & \ttrans[\rulet_1] \arrow \ttrans[\rulet_2] &
\ttrans[\rulet_1 \iarrow \rulet_2] & = & \ttrans[\rulet_1] \arrow \ttrans[\rulet_2] %\\
\end{array}
\end{equation*}
Its reveals that implicit $\name$ arrows are translated to explicit System F function arrows.

@@

For simple types $\type$ rule \rref{R-Simp} delegates the work of
building evidence, when a matching rule $\rulet$ type is found in the
environment, to rule \rref{L-RuleMatch}. The evidence consists of two parts:
$E$ is the evidence of matching $\type$ against $\rulet$. This match contains
placeholders $\bar{x}$ for the contexts whose resolution is postponed by rule
\rref{M-IAbs}. It falls to rule \rref{L-RuleMatch} to perform these
postponed resolutions, obtain their evidence $\bar{E}$ and fill in the
placeholders.

@@

\begin{theorem}[Type-Preserving Translation]\label{thm:type:preservation} Let $e$ be a $\name$
  expression, $\rulet$ be a type, $\tenv$ be a type environment and $E$ be a System F expression. If
  $\wte{\tenv}{e}{\rulet}{E}$, then $\fwte{\etrans{\tenv}}{E}{\ttrans[\rulet]}$.
\end{theorem}
Here we define the translation of the type environment form $\name$ to System F as:
\begin{equation*}
\begin{array}{rcl@{\hspace{2cm}}rcl}
\etrans{\epsilon} & = & \epsilon & \etrans{\tenv,\alpha} & = & \etrans{\tenv}, \alpha \\
\etrans{\tenv,x : \rulet} & = & \etrans{\tenv}, x : \ttrans[\rulet] &
\etrans{\tenv, \rulet \leadsto x} & = & \etrans{\tenv}, x : \ttrans[\rulet]
\end{array}
\end{equation*}

@@

\begin{theorem}[Partial Correctness]
Let $\tenv$ be a type environment, $\rulet$ be a type and E be a System F expression.
Assume that $\unambig{\epsilon}{\rulet}$ and also $\forall \rulet_i \in \tenv: \unambig{\epsilon}{\rulet_i}$.
Then $\dres{\tenv}{\rulet}{E}$ if and only if $\adres{\tenv}{\rulet}{E}$,
provided that the algorithm terminates.
\end{theorem}

>>>>

The function $\ttrans$ takes 
$\name$ types $\rulet$ to System F types T: 
\begin{equation*}
\begin{array}{rcl@{\hspace{1cm}}rcl}
\ttrans[\alpha] & = & \alpha &
\ttrans[\forall \alpha. \rulet] & = & \forall \alpha. \ttrans[\rulet] \\
\ttrans[\rulet_1 \arrow \rulet_2] & = & \ttrans[\rulet_1] \arrow \ttrans[\rulet_2] &
\ttrans[\rulet_1 \iarrow \rulet_2] & = & \ttrans[\rulet_1] \arrow \ttrans[\rulet_2] %\\
\end{array}
\end{equation*}
It reveals that implicit $\name$ arrows are translated to explicit System F function arrows.

@@

For simple types $\type$ rule \rref{R-Simp} delegates the work of
building evidence, when a matching implicit $\rulet$ is found in the
environment, to rule \rref{L-RuleMatch}. The evidence consists of two parts:
$E$ is the evidence of matching $\type$ against $\rulet$. This match contains
placeholders $\bar{x}$ for the contexts whose resolution is postponed by rule
\rref{M-IAbs}. It falls to rule \rref{L-RuleMatch} to perform these
postponed resolutions, obtain their evidence $\bar{E}$ and fill in the
placeholders.

@@

\begin{theorem}[Type-Preserving Translation]\label{thm:type:preservation} Let $e$ be a $\name$
  expression, $\rulet$ be a type, $\tenv$ be a type environment and $E$ be a System F expression. If
  $\wte{\tenv}{e}{\rulet}{E}$, then $\fwte{\etrans{\tenv}}{E}{\ttrans[\rulet]}$.
\end{theorem}
Here we define the translation of the type environment form $\name$ to System F as:
\begin{equation*}
\begin{array}{rcl@{\hspace{2cm}}rcl}
\etrans{\epsilon} & = & \epsilon & \etrans{\tenv,\alpha} & = & \etrans{\tenv}, \alpha \\
\etrans{\tenv,x : \rulet} & = & \etrans{\tenv}, x : \ttrans[\rulet] &
\etrans{\tenv, \envi{\rulet}{x}} & = & \etrans{\tenv}, x : \ttrans[\rulet]
\end{array}
\end{equation*}

@@

\begin{theorem}[Partial Correctness]
Let $\tenv$ be a type environment, $\rulet$ be a type and E be a System F expression.
Assume that $\unambig{\epsilon}{\rulet}$ and also $\forall \rulet_i \in \tenv: \unambig{\epsilon}{\rulet_i}$.
Then $\dres{\tenv}{\rulet}{E}$ if and only if $\adres{\tenv}{\rulet}{E}$.
\end{theorem}
